%-------------------------
% Resume in Latex
% Author : andythropic
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[scaled]{helvet}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{xcolor} % for custom named colors

% Define your accent color here:
\definecolor{AccentColor}{RGB}{0, 32, 96} % Navy Blue
% Or use: {RGB}{0, 100, 0} for Dark Green
% Or use: {RGB}{128, 0, 32} for Burgundy

\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}
  {\color{AccentColor}\vspace{-4pt}\scshape\raggedright\large}
  {}{0em}{}[\color{AccentColor}\titlerule \vspace{-5pt}]

\pdfgentounicode=1
\titlespacing*{\section}{0pt}{4pt plus 1pt minus 1pt}{10pt plus 1pt minus 1pt}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2
  \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,itemsep=0pt,topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape \textcolor{AccentColor}{\textbf{PHAM DUC LONG}}} \\ \vspace{1pt}
    \small
    \href{mailto:longphamk2@gmail.com}{longphamk2@gmail.com} $|$
    \href{https://www.linkedin.com/in/pdlong21}{https://www.linkedin.com/in/pdlong21} $|$
    0332481087 $|$
    \href{https://github.com/pdlong4002}{github.com/pdlong4002}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Van Hien University}{Expected 2026}
    {B.Sc. in Computer Science -- Software Engineering | GPA: 3.2/4}{Ho Chi Minh City, Vietnam}
    \resumeItemListStart
      \resumeItem{Relevant Coursework: Data Structures \& Algorithms, Database Systems, System Analysis \& Design, Web Programming}
      \resumeItem{Clubs: Competitive Programming Club -- OLP/ICPC Training Team}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
    {Software Tester}{Feb 2026 -- May 2026}
    {HiAI Company}{Ho Chi Minh City, Vietnam}
    \resumeItemListStart
      \resumeItem{Performed manual testing for web applications to identify functional defects and usability issues.}
      
      \resumeItem{Designed and executed test cases based on software requirements and user workflows.}
      
      \resumeItem{Tested RESTful APIs using Postman to validate request/response data and backend functionality.}
      
      \resumeItem{Reported, tracked, and verified bugs using Jira with detailed reproduction steps and expected results.}
      
      \resumeItem{Collaborated with developers to reproduce issues, retest fixes, and improve software quality before release.}
      
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Mini E-Commerce Backend System} $|$ \emph{Java, Spring Boot, MySQL, JPA/Hibernate, VNPay}}{2025}
    \resumeItemListStart
      \resumeItem{Developed a backend system supporting product management, orders, and payment workflows.}
      \resumeItem{Integrated VNPay payment gateway with secure HMAC-SHA512 signature verification.}
      \resumeItem{Applied DTO pattern, request validation, and global exception handling for a robust architecture.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Question Platform Backend System} $|$ \emph{Java, Spring Boot, JWT, MySQL, JPA/Hibernate}}{2026}
    \resumeItemListStart
      \resumeItem{Built a Q\&A platform backend supporting user interactions, nested comments, and moderation.}
      \resumeItem{Implemented JWT authentication with role-based access control (USER/ADMIN) for secure access.}
      \resumeItem{Designed relational database schemas and entity relationships to ensure data integrity and performance.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------ACTIVITIES-----------
\section{Activities}
\resumeSubHeadingListStart

  \resumeSubheading
    {ICPC Competitive Programming Team}{2024 -- Present}
    {Van Hien University}{Ho Chi Minh City, Vietnam}
    \resumeItemListStart
      \resumeItem{Participated in algorithmic problem-solving training and competitive programming contests.}
      \resumeItem{Practiced data structures, algorithms, and problem-solving techniques for ICPC/OLP competitions.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{

\textbf{Languages}: Java, C++, Python, JavaScript, SQL \\

\textbf{Frontend}: HTML, CSS, Bootstrap, Thymeleaf \\

\textbf{Backend}: Spring Boot, Spring MVC, Spring Security, REST APIs, (Jwt/OAuth2), JPA/Hibernate, Apache Kafka \\

\textbf{Databases}: MySQL, MongoDB, Redis \\

\textbf{Tools \& CI/CD}: Git, GitHub, Docker, Postman, Swagger, GitHub Actions

}}
\end{itemize}

% ---------- ACHIEVEMENTS ----------
\section{Certifications}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Olympic Tin Hoc Sinh Vien Viet Nam}}{2025}
  \resumeProjectHeading
    {\textbf{ICPC Asia Regional Contest} $|$ \emph{Ho Chi Minh City Site}}{2025}
\resumeSubHeadingListEnd

\end{document}